### 2017-12-05 submission/manuscript.Rmd
update title
add comparison tables to be used

@@

# Insert Title Here

>>>>

# Read in fecal sample number of OTU results
fs_anova_summary <- read_csv("../data/process/tables/fecal_overall_anova_results.csv")
fs_tukey_summary <- read_csv("../data/process/tables/fecal_overall_tukey_results.csv")

# Read in error rate results
krsukal_error_rate <- read_csv("../data/process/tables/mock_error_overall_kruskal_results.csv")
dunn_error_rate <- read_csv("../data/process/tables/mock_error_overall_dunn_results.csv")

@@

# What the Taq? The Influence of Different Hi-Fidelity Taq Polymerase on 16S rRNA Sequencing
